---
title: "Maps in R"
author: "Matthew Malcher"
date: "8 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction
In this markdown document I will investigate methods and packages for creating maps in R. This is a WIP and the intent is that it acts as a personal knowledge base for mapping in R.

# List of Tutorials

## Trafford Data Lab
https://medium.com/@traffordDataLab/lets-make-a-map-in-r-7bd1d9366098

* sf
* tidyverse
* classInt 
* viridis

### Get Local Authority Boundaries

The ONS Open Geography Portal is one of the best places for UK shapefiles. You can get URL's for geojson's from the `API` dropdown on each page.

```{r}
require(sf)
UK_LA_SuperGen_Clipped <- "https://opendata.arcgis.com/datasets/ae90afc385c04d869bc8cf8890bd1bcd_3.geojson"
UKLA <- st_read(dsn=UK_LA_SuperGen_Clipped)
```

```{r Simple Plot }
plot(st_geometry(UKLA))
```

```{r}
#We can also read in the lookup tables from ONS using st_read - these just have an empty list instead of a set of points for each item.
LAD2Country <- st_read(dsn="https://opendata.arcgis.com/datasets/ffbb56e049b145a28720f0d817d6c197_0.geojson")

st_geometry(LAD2Country) <- NULL

```

## Join to Other Data

```{r}
require(dplyr)
LA_with_Country <- left_join(UKLA,LAD2Country, by="")
```

# Other useful links

## Spatial Joins!
https://r-spatial.github.io/sf/reference/st_join.html

#Tidyverse sf things
http://strimas.com/r/tidy-sf


## Reproducible Research Course
The final lecture of the [http://eriqande.github.io/rep-res-web/syllabus.html](Reproducible reasearch course) looks at severa differnt mapping methods for making maps with R. Note that this page is also available as an RMD. 
https://eriqande.github.io/rep-res-web/lectures/making-maps-with-R.html


https://blog.exploratory.io/creating-geojson-out-of-shapefile-in-r-40bc0005857d

## Leaflet
From the people at RStudion - a section of the leaflet tutorial dealing with maps.
https://rstudio.github.io/leaflet/json.html

Packages
* rgdal
* geojsonio#

## UK Data Service
Tutorial from the UK data service on how to produce maps of census data using R
https://www.ukdataservice.ac.uk/media/604930/mapping-2011-census-microdata-using-r.pdf

Packages:
* rgdal
* tmap
* dplyr
* data.table


## Kev Johnson
A blogger who seems to know whats up
http://www.kevjohnson.org/making-maps-in-r/

Packages:
* ggplot2
* rgdal: reads in shape files
* scales: tells ggplot what the proper scale should be
* ggmap: comes with a nice theme_nothing() function
* dplyr: for left_join()
* Cairo: creates high quality vector and bitmap images